### 2018-10-06 VV556/HW3/submission.tex
ex2 ok

@@

\section{Exercise3.2}

\section{Exercise3.3}

>>>>

\usepackage{graphicx}

@@

\section{Exercise3.2}
	\begin{enumerate}
		\item 
			Consider the projection of $f(x)$ onto $P_0(x)$, $P_1(x)$ and $P_2(x)$ correspondingly
			\begin{equation}
				(f, P_0) = \int_{-1}^{1} e^x dx = e - \frac{1}{e}
			\end{equation}

			\begin{equation}
				(f, P_1) = \int_{-1}^{1} x e^x dx = \frac{2}{e}
			\end{equation}

			\begin{equation}
				(f, P_2) = \int_{-1}^{1} \frac{3x^2 -1}{2} e^x dx = e - \frac{7}{e}
			\end{equation}
			As $(P_i, P_j)=0$ when $i \neq j$, $p(x)$ can be written as linear combination of $P_i$
			\begin{equation}
				p(x) = a_0 P_0(x) + a_1 P_1(x) + a_2 P_2(x)
			\end{equation}
			with coefficient $a_i$ given as
			\begin{equation}
				a_i = \frac{(f, P_i)}{(P_i, P_i)} = \frac{2i+1}{2} (f, P_i)
			\end{equation}
			Finally
			\begin{equation}
				p(x) = 1.1752 P_0(x) + 1.1036 P_1(x) + 0.3578 P_2(x)
			\end{equation}

		\item 
		The plot(Fig \ref{fig:comp}) is provided for comparsion.

		\begin{figure}[!htbp]
			\centering
			\includegraphics[]{ApproximationCompare.png}
			\caption{Comparsion of different approximation for $e^x$}
			\label{fig:comp}
		\end{figure}

		The distinction is quite obvious and Legendre polynomials does better than taylor series expansion at zero point.

	\end{enumerate}

\section{Exercise3.3}
	\begin{enumerate}
		\item

		\item

	\end{enumerate}
